---
title: "Conditional probability using simulation"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

#### Execute the following cells to load the libraries
```{r}
library(ggplot2)
library(dplyr)
```


#### Load the bats data to a dataframe
```{r}
dBat = read.csv('Data/bats.csv', row.names=1, header = TRUE, stringsAsFactors = TRUE)
head(dBat)
```

```{r}
#dBat(1, c[Gene.1,Gene.2,Gene.3,Gene.4,Gene.5,Ebola])
#dBat %>% filter() %>% select(Gene.1,Gene.2,Gene.3,Gene.4,Gene.5,Ebola)
dBat[1, c("Gene.1", "Gene.2", "Gene.3", "Gene.4", "Gene.5", "Ebola")]
```


##### Get the genes that are expressed for the 1st bat
```{r}
dBat %>% select(Gene.1,Gene.2,Gene.3,Gene.4,Gene.5,Ebola)

```

#### Probability that a random bat carries the Ebola virus
```{r}

```

#### Probability that gene-1 through gene-5 is expressed in a random bat
```{r}

```

#### Is expression of gene-1 through gene-5 dependent or independent of the bat carrying the Ebola virus
```{r}
# Subset the dataframe to those bats that carry the Ebola virus


# Conditional probability that gene-1 through gene-5 is expressed
# given that the bat carries the Ebola virus

```

#### Probability that a random bat carries the Ebola given that gene-3 through gene-5 is expressed
```{r}


```

