---
title: "Quantifying uncertainty using simulation"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

#### Execute the following cells to load the libraries
```{r}
library(ggplot2)
library(dplyr)
```

#### Sampling space and likelihood vector
```{r}
s = c('H', 'T')
p = c(0.5, 0.5)
```


#### Function to simulate one trial of the random experiment which in this case is tossing 10 fair coins at a time
```{r}
simTrial = function(){
  return(sample(s, 10, replace = TRUE, prob = p))
}
```

#### Replicate the trials of the random experiment a large number of times
```{r}
nsimulations = 10000
simulatedData = replicate(nsimulations, simTrial())
```

#### Function to check if event of interest has occured which in this case is getting exactly 3 heads
```{r}
checkEvent = function(data){
  return(sum(data == 'H') == 3)
}
```

#### Calculate the fraction of times the event of interest occured which is what we define as the approximate probability of the event E happening in the next trial of the random experiment
```{r}
#simulatedData
mean(apply(simulatedData, 2, checkEvent))
```

```{r}
courtData= read.csv('Data/court.csv')
head(courtData,5)
```

```{r}
simtrialJudge = function(n){
  jcp= apply(courtData,2,mean)
  jcip=1-jcp
  s=c(1,0)
  court_decision= vector('integer',n)
  for(j in 1:n){
    court_decision[j]=sample(s,1,p=c(jcp[j],jcip[j]))
  }
  return(court_decision)
}
```

```{r}
checkEventJudge = function(data){
  if(sum(data)<=2){
    return (1)
  }
  else{
    return (0)
  }
}
```

```{r}
simulateData= replicate(10000, simtrialJudge(5))
print(simulateData)
apply(simulateData,2, checkEventJudge)
mean(apply(simulateData,2, checkEventJudge))
```

###Birthday problem

```{r}
simtrialBirthday = function(n){
  return(sample(1:365, 60, replace=TRUE, prob=replicate(365,1/365)))
}
simtrialBirthday(60)
```

```{r}
#checkEventBirthday = function(data){
 # if(sum(data)>= 2){
  #  return (1)
  #}
  #else{
  #  return (0)
  #}
#}
checkEventBirthday = function(data) {
  num_students = length(data)
  for (i in 1:(num_students - 1)) {
    for (j in (i + 1):num_students) {
      if (data[i] == data[j]) {
        return (1)
      }
    }
  }
  return (0)  
}

```

```{r}
simulateBirthday= replicate(10000, simtrialBirthday(60))
apply(simulateBirthday,2, checkEventBirthday)
probability=mean(apply(simulateBirthday,2, checkEventBirthday))
print(probability)
```

